Do researchers preferentially collaborate with colleagues of the same gender?

### 2018-06-07 Gender_homophily_analysis.Rmd
Small tweaks

```{r fig.width=6, fig.height=5}
model <- summary(lm(alpha.adjusted ~ standardised.IF, data = master.dataset %>% 
                      filter(Age == "New", 
                             Subset == "All authors", 
                             !is.na(standardised.IF))))
R2 <- model$adj.r.squared %>% 
        round(3) %>% format(nsmall = 3)

>>>>

```{r fig.width=6, fig.height=5}
model <- summary(lm(alpha.adjusted ~ scale(standardised.IF), data = master.dataset %>% 
                      filter(Age == "New", 
                             Subset == "All authors", 
                             !is.na(standardised.IF))))
R2 <- model$adj.r.squared %>% 
        round(3) %>% format(nsmall = 3)
